---
title: "Partially Linear Model"
output: html_notebook
---

Data: $\{Y_i, X_{i1}, X_{i2}, \dots, X_{id}, i=1,2,\dots,n\}$  
Partially Linear Model: $Y_i = \eta_0(T_i) + X_i^T\beta_0+\epsilon_i$, $X=(X_1,\dots,X_p)^T \in R^{\ p}, T\in R^{\ d-p}$

```{r}
# generate data
set.seed(123)
n = 50
X = matrix(c(rnorm(n, 5, 10), rnorm(n), rnorm(n, 3, 3), rbeta(n, 2.2, 0.6), rgamma(n, 1.6), runif(n, 0, 20)), nrow=n)
Y = apply(X, 1, function(X){0.5*(X[1])^2 + 3*X[2] + 3*X[3] + 4*X[4] + 4*X[5] + 5*X[6] })
pairs(cbind(Y,X))
```

### Model 1: Two-Step Estimation, Assume dim(T) = 1  
Model: $Y = \eta_0 + X \beta_0 + \epsilon$  
Step 1: nonparametric profiled estimation.    
 Suppose $\beta_0=\beta$ is given, $Y-X\beta=\eta_0 + \epsilon$, then $\hat{\eta}_0 = S_b(Y-X\beta)$, where $S_b$ is the smoothing matrix.      
Step 2:  parametric estimation.     
$Y \approx S_b(Y-X\beta) + X\beta + \epsilon$    
$(I-S_b)Y \approx (I-S_b)X\beta + \epsilon$   
then $\hat{\beta} = \hat{\beta}_{LSE} = [X^T(I-S_b^T)(I-S_b)X]^{-1}[X^T(I-S_b^T)(I-S_b)Y]$     
and $\hat{\eta}_\beta = S_b(Y-X\hat{\beta})$  
$\sqrt{n}(\hat{\beta}_{2s}-\beta) \xrightarrow{d}N(0, \sigma^2_{\epsilon}[E\{Var(Z|X)\}]^{-1}) $





### Model 2: An elementary estimator of PLM, Assume dim(T) <= 3  

Yatchew, Adonis. "An elementary estimator of the partial linear model." Economics letters 57.2 (1997): 135-143.   

Model: $Y = Z^T\beta + f(X) + \epsilon$, $X=(X_1,X_2,\dots,X_k)^T, k \le 3$, $Z=(Z_1,Z_2,\dots,Z_p)^T$    
Motivation from $k=1$, assume $X_1 \le X_2 \le \dots \le X_n$,    
then $Y_i - Y_{i-1} = (Z_i^T-Z_{i-1}^T)\beta + (f(X_i)-f(X_{i-1})) + (\epsilon_i - \epsilon_{i-1}) \approx (Z_i^T-Z_{i-1}^T)\beta + \epsilon^*$, because $X_{(i)}-X_{(i-1)} = O_p(\frac{1}{n})$   
then, $\hat{\beta}_{diff}=(Z^*Z^*)^{-1}(Z^*Y^*)$   
And $\sqrt{n}(\hat{\beta}_{diff} - \beta) \xrightarrow{d} N(0, 1.5\sigma^2_{\epsilon}[E\{Var(Z|X)\}]^{-1})$   


```{r}
Y = Y[order(X[,1])]
X = X[order(X[,1]),]
diffY = Y[2:length(Y)] - Y[1:(length(Y)-1)]
diffX = X[2:nrow(X),] - X[1:(nrow(X)-1),]
diffX = diffX[,-1]
model1 = lm(diffY ~ 0 + diffX)
resF = (Y - X[,-1] %*% model1$coefficients)
plot(resF ~ X[,1])
```



